Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/paper.Rmd
Add more detail on inter-rater repeatability including sup figure

@@

@@

## Figures

@@

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
))
```

@@

>>>>

Looking at the ratings for all 450 articles and given the differing number of articles each co-author evaluated, there was broad agreement with no discernible patterns showing a strong bias or cause for concern (Figure \@ref(fig:evaluator-differences)).
However, the analyses did account for different raters for each article by including this as a random effect.

@@

Our goal was to evaluate as many articles as we realistically could to get as broad an overview of the discipline as possible.
Because of this each article, save the five that were used to compare the inter-rater differences, was evaluated by only one co-author.

@@

## Supplementary Figures

```{r evaluator-differences, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Criteria scores for 450 articles computational materials and data avaialbility for each of the five evaluators. Each article was evaluated on a 0 to 3 scale for computational materials (Code) and raw data availability (Data) by one of five evaluators."}
p <- import_notes() %>%
  mutate(
    comp_mthds_avail = as.numeric(as.character(comp_mthds_avail)),
    data_avail =  as.numeric(as.character(data_avail))
  ) %>%
  pivot_longer(cols = c("comp_mthds_avail",
                        "data_avail")) %>%
  ggplot(aes(y = as.factor(value), x = assignee)) +
  geom_count() +
  ylab("Criteria Score") +
  xlab("Evaluator") +
  ggtitle("Criteria scores by evaluator") +
  facet_wrap(name ~ .,
             labeller = labeller(name =
                                   c(
                                     "comp_mthds_avail" = "Code",
                                     "data_avail" = "Data"
                                   )))

ggsave(
  filename = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
  outfile = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"),
  options = "-dEPSCrop"
)
include_graphics(path = here("analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"))
```

@@

@@

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_7.eps"
))
```
